Bird beak's elaboration and innovation

### 2022-07-21 Analysis/03-Elaboration_innovation_analysis.Rmd
EI at species vs group level figure

>>>>

```{r}
## Distribution of elaboration and innovation at the species level
elaboration_species      <- get.disparity(get.subsets(results$super_results_phylo$position, subsets = "phylogeny"), concatenate = FALSE)[[1]]
innovation_species       <- get.disparity(get.subsets(results$super_results_phylo$distance, subsets = "phylogeny"), concatenate = FALSE)[[1]]

## Distribution of elaboration and innovation at the group level
scale.group <- function(X) return(X/max(X))
elaboration_super_orders <- lapply(get.disparity(results$super_results_between$position, concatenate = FALSE), scale.group)
innovation_super_orders  <- lapply(get.disparity(results$super_results_between$distance, concatenate = FALSE), scale.group)
elaboration_orders       <- lapply(get.disparity(results$order_results_between$position, concatenate = FALSE), scale.group)
innovation_orders        <- lapply(get.disparity(results$order_results_between$position, concatenate = FALSE), scale.group)

## Plot all that
plot.density <- function(species, group, main, scale.x = TRUE, scale.y = TRUE, col = c("blue", "orange")) {
    scale.xy <- function(density, x = FALSE, y = TRUE) {
        if(x) {
            density$x <- density$x/max(density$x)
        }
        if(y) {
            density$y <- density$y/max(density$y)
        }
        return(density)
    }
    den_sp    <- scale.xy(density(species), x = scale.x, y = scale.y)
    den_group <- scale.xy(density(group), x = scale.x, y = scale.y)

    plot(NULL, xlim = range(c(den_sp$x, den_group$x)), ylim = range(c(den_sp$y, den_group$y)), xlab = main, ylab = "density")
    lines(den_sp, col = col[1])
    lines(den_group, col = col[2])
}

pdf("../Manuscript/Figures/Relative_EI.pdf", height = 12, width = 6)
par(mfrow = c(2,1))
plot.density(species = c(elaboration_species),
             group   = c(unlist(elaboration_super_orders), unlist(elaboration_orders)),
             main    = "relative elaboration", scale.x = TRUE)
plot.density(species = c(innovation_species),
             group   = c(unlist(innovation_super_orders), unlist(innovation_orders)),
             main    = "relative innovation", scale.x = TRUE)
legend("topright", lty = 1, legend = c("species", "groups"), col = c("blue", "orange"))
dev.off()
```
